\vspace{-1in} \usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{CSEC-472 Authentication Paper} \\ [14pt] \huge A Security Analysis of the Lenel BlueDiamond \\

### 2020-05-06 paper/paper/paper.tex

\section{Preliminary Suppositions \& Implications}
Words

\subsection{Theoretical Implications}
Words

\subsection{Practical Implications}
Words

>>>>

\section{Preliminary Suppositions \& Implications}
This reasearch will expand and refine on the current work available on Lenel readers and readers in general. While we could find several research papers on BLE lock examination \cite{matthewrs2017surveydoorlock}\cite{ho2016smart}\cite{ye2017security}\cite{8887393}, we found no research on readers that offer multiple protocols for communication. We have a opportunity to add insight on examining mutli-protocol readers and how to approached examining and attacking them. In addition, we could find very little on attack chains for RFID or Wiegand based attacks \cite{chung2017wiegand}. Our work will allow for the creating of a preliminary attack chain for these protocols.

Existing attack chains against BLE will also be refined. We have seen these chains demonstrated \cite{lonzetta2018security}\cite{BluetoothMITMTal} already, but not laid out and explored beyond simply using the tools. These processes and procedures can be laid out and refined in this research allowing for a properly documented attack chain.

Finally, the security of the Lenel BlueDiamond will be affirmed. Our testing will allow for third party confirmation that these devices are secure against attacks. Lenel will benefit from outsider knowledge that is not present in institutional knowledge.
